Fusion Moves for Correlation Clustering

### 2014-11-14 paper/egpaper_for_review.tex
uv to ij

\subsection{Fast Optimization of CC-Fusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{l_v(y)|v\in V\}$, $E_y=\{l_u(y)l_v(y)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, l_u(y)=\bar{u},l_v(y)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$ by
%
\begin{align}
\tilde{y}_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{l_u(y)l_v(y)}& \textrm{ if }l_u(y) \neq l_v(y)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}

>>>>

\subsection{Fast Optimization of CC-Fusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is, as for classical fusion~\cite{Lempitsky-2010}, NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ and a segmentation of $G$ given by $y\in P(G)$,
we define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{l_i(y)|i\in V\}$, $E_y=\{l_i(y)l_j(y)|ij\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{ij\in E, l_i(y)=\bar{u},l_j(y)=\bar{v}}w_{ij}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $\tilde{y}$ of the original graph $G=(V,E)$ by
%
\begin{align}
\tilde{y}_{ij}&=\left\{ 
\begin{array}{ll}
\bar{y}_{l_i(y)l_j(y)}& \textrm{ if }l_i(y) \neq l_j(y)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}
